Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 introduction.tex
Removed fluff in paragraph 1 of section 1.1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1182 ccdd05d5-56c1-461a-bf98-85f6876523b4

Though compact binary coalescence (\CBC{}) events may be responsible for
several classes of \EM{} transients, \CBC{}s are in particular believed to be a
mechanism for short gamma-ray bursts (short \GRB{}s) \citep{Lee:2005, nakar07}.
In this scenario, prompt gamma-ray emission arises on the accretion timescale
of a central compact object formed after the merger, $0.1$--$1.0$\,s
\citep{Janka1999}.  Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with
ejecta \citep{Bucciantini2011}.  In the case of the proto-magnetar, it might be
formed from accretion-induced collapse, or the merger of two \textsc{ns}s.  An
accompanying \GW{} observation would confirm the latter.

>>>>

Compact binary coalescence (\CBC) is thought to be a
mechanism for short gamma-ray bursts (short \GRB{}s) \citep{Lee:2005, nakar07}.
In this scenario, prompt gamma-ray emission arises on the accretion timescale
of a central compact object formed after the merger, $0.1$--$1.0$\,s
\citep{Janka1999}.  Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with
ejecta \citep{Bucciantini2011}.  In the case of the proto-magnetar, it might be
formed from accretion-induced collapse, or the merger of two \textsc{ns}s.  An
accompanying \GW{} observation would confirm the latter.
